### 2025-05-11 front_materials/abstract.tex
Finished rough-draft of introduction

The first project proposes a novel approach for performing inference on Auto Regressive Moving Average (ARMA) time series models, which are formally linearly Gaussian state space models.
ARMA models are among the most frequently taught and widely used methods for time series analysis.
In this project, I demonstrate that existing algorithms and software for parameter estimation often produce sub-optimal parameter estimates with surprising frequency.
I introduce a novel random initialization algorithm designed to leverage the structure of the ARMA likelihood function to help overcome these optimization shortcomings.
Additionally, I demonstrate that profile likelihoods offer superior confidence intervals compared to those based on the Fisher information matrix, which is the current standard practice for ARMA modeling.

>>>>

The first project proposes a novel approach for performing inference on Auto Regressive Moving Average (ARMA) time series models, which are formally linearly Gaussian state space models.
ARMA models are among the most frequently taught and widely used methods for time series analysis.
In this project, I demonstrate that existing algorithms and software for parameter estimation often produce sub-optimal parameter estimates with surprising frequency.
I introduce a novel random initialization algorithm designed to leverage the structure of the ARMA likelihood function to help overcome these optimization shortcomings.
Additionally, I demonstrate that profile likelihoods offer superior confidence intervals compared to those based on the Fisher information matrix---the current standard practice for ARMA modeling.
